Capstone Movielens Report

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function's description: `train_UMGY_SmoothedDay_effect.cv`.

::: {.noteblock data-latex=""}
This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively). The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
:::

@@

Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments..

>>>>

@@

Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments.

This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively). The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
